rgbif: R client for working with GBIF species occurrence data

### 2015-10-06 manuscript.Rmd
dont run occ_download
edits, rendered ms

```{r compile-settings, include=FALSE}
library("methods")
library("knitr")
opts_chunk$set(tidy = FALSE, warning = FALSE, message = FALSE,
               cache = 1, comment = NA, verbose = TRUE)
basename <- gsub(".Rmd", "", knitr:::knit_concord$get('infile'))
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
```

@@

```{r}
occ_download('taxonKey = 3119195')
```

@@

@@

>>>>

```{r compile-settings, include=FALSE}
library("methods")
library("knitr")
opts_chunk$set(
  tidy = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = 1,
  comment = '#>',
  collapse = TRUE,
  verbose = TRUE
)
basename <- gsub(".Rmd", "", knitr:::knit_concord$get('infile'))
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
```

@@

```{r eval = FALSE}
occ_download('taxonKey = 3119195')
#> <<gbif download>>
#>   Username: xxxx
#>   E-mail: xxxx
#>   Download key: 0000840-150615163101818
```

@@

### A

### B

### C

@@

* pt 1
* pt 2
* pt 3
* pt 4

### 2015-10-06 manuscript.tex
edits, rendered ms

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res <-}\StringTok{ }\KeywordTok{dataset_search}\NormalTok{(}\DataTypeTok{query =} \StringTok{"oregon"}\NormalTok{)}
\NormalTok{res$data$datasetTitle[}\DecValTok{1}\NormalTok{:}\DecValTok{10}\NormalTok{]}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
 [1] "SDNHM Birds Collection"                                                
 [2] "CM Birds Collection"                                                   
 [3] "condoncollection"                                                      
 [4] "Taxonomy in Flux Checklist"                                            
 [5] "Wool carder bees of the genus Anthidium in the Western Hemisphere"     
 [6] "Bryophyte Collection - University of Washington Herbarium (WTU)"       
 [7] "University of British Columbia Herbarium (UBC) - Bryophytes Collection"
 [8] "UWFC Ichthyology Collection"                                           
 [9] "Lichen Collection - University of Washington Herbarium (WTU)"          
[10] "UWBM Mammalogy Collection"                                             
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{networks}\NormalTok{(}\DataTypeTok{limit=}\DecValTok{10}\NormalTok{)$data$title}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
 [1] "GBIF Backbone Sources"                                      
 [2] "Canadensys"                                                 
 [3] "Southwest Collections of Arthropods Network (SCAN)"         
 [4] "VertNet"                                                    
 [5] "Dryad"                                                      
 [6] "GBIF Network"                                               
 [7] "The Knowledge Network for Biocomplexity (KNB) "             
 [8] "Online Zoological Collections of Australian Museums (OZCAM)"
 [9] "Catalogue of Life"                                          
[10] "Ocean Biogeographic Information System (OBIS)"              
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{occ_download}\NormalTok{(}\StringTok{'taxonKey = 3119195'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
<<gbif download>>
  Username: sckott
  E-mail: myrmecocystus@gmail.com
  Download key: 0004098-150922153815467
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{(res <-}\StringTok{ }\KeywordTok{occ_download_get}\NormalTok{(}\StringTok{"0000840-150615163101818"}\NormalTok{, }\DataTypeTok{overwrite =} \OtherTok{TRUE}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
<<gbif downloaded get>>
  Path: ./0000840-150615163101818.zip
  File size: 3.19 MB
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(}\StringTok{"dplyr"}\NormalTok{)}
\NormalTok{dat <-}\StringTok{ }\KeywordTok{occ_download_import}\NormalTok{(res)}
\NormalTok{dat %>%}
\StringTok{  }\KeywordTok{select}\NormalTok{(gbifID, decimalLatitude, decimalLongitude)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
      gbifID decimalLatitude decimalLongitude
1  657590544              NA               NA
2  657679551              NA               NA
3  657791316        37.70805        -118.4162
4  658180562              NA               NA
5  441881672              NA               NA
6  911596181              NA               NA
7   56454601              NA               NA
8  657848913              NA               NA
9  658187373              NA               NA
10 658279212        38.95917        -106.9892
..       ...             ...              ...
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{out <-}\StringTok{ }\KeywordTok{occ_search}\NormalTok{(}\DataTypeTok{issue=}\StringTok{'DEPTH_UNLIKELY'}\NormalTok{, }\DataTypeTok{limit =} \DecValTok{500}\NormalTok{)}
\KeywordTok{NROW}\NormalTok{(out)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
[1] 4
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{out %>%}\StringTok{ }\KeywordTok{occ_issues}\NormalTok{(-cudc) %>%}\StringTok{ }\NormalTok{.$data %>%}\StringTok{ }\NormalTok{NROW}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
[1] 2
\end{verbatim}

@@

@@

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res <-}\StringTok{ }\KeywordTok{dataset_search}\NormalTok{(}\DataTypeTok{query =} \StringTok{"oregon"}\NormalTok{)}
\NormalTok{res$data$datasetTitle[}\DecValTok{1}\NormalTok{:}\DecValTok{10}\NormalTok{]}
\CommentTok{#>  [1] "SDNHM Birds Collection"                                                }
\CommentTok{#>  [2] "CM Birds Collection"                                                   }
\CommentTok{#>  [3] "condoncollection"                                                      }
\CommentTok{#>  [4] "Taxonomy in Flux Checklist"                                            }
\CommentTok{#>  [5] "Wool carder bees of the genus Anthidium in the Western Hemisphere"     }
\CommentTok{#>  [6] "Bryophyte Collection - University of Washington Herbarium (WTU)"       }
\CommentTok{#>  [7] "University of British Columbia Herbarium (UBC) - Bryophytes Collection"}
\CommentTok{#>  [8] "UWFC Ichthyology Collection"                                           }
\CommentTok{#>  [9] "Lichen Collection - University of Washington Herbarium (WTU)"          }
\CommentTok{#> [10] "UWBM Mammalogy Collection"}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{networks}\NormalTok{(}\DataTypeTok{limit=}\DecValTok{10}\NormalTok{)$data$title}
\CommentTok{#>  [1] "GBIF Backbone Sources"                                      }
\CommentTok{#>  [2] "Canadensys"                                                 }
\CommentTok{#>  [3] "Southwest Collections of Arthropods Network (SCAN)"         }
\CommentTok{#>  [4] "VertNet"                                                    }
\CommentTok{#>  [5] "Dryad"                                                      }
\CommentTok{#>  [6] "GBIF Network"                                               }
\CommentTok{#>  [7] "The Knowledge Network for Biocomplexity (KNB) "             }
\CommentTok{#>  [8] "Online Zoological Collections of Australian Museums (OZCAM)"}
\CommentTok{#>  [9] "Catalogue of Life"                                          }
\CommentTok{#> [10] "Ocean Biogeographic Information System (OBIS)"}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{occ_download}\NormalTok{(}\StringTok{'taxonKey = 3119195'}\NormalTok{)}
\CommentTok{#> <<gbif download>>}
\CommentTok{#>   Username: xxxx}
\CommentTok{#>   E-mail: xxxx}
\CommentTok{#>   Download key: 0000840-150615163101818}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{(res <-}\StringTok{ }\KeywordTok{occ_download_get}\NormalTok{(}\StringTok{"0000840-150615163101818"}\NormalTok{, }\DataTypeTok{overwrite =} \OtherTok{TRUE}\NormalTok{))}
\CommentTok{#> <<gbif downloaded get>>}
\CommentTok{#>   Path: ./0000840-150615163101818.zip}
\CommentTok{#>   File size: 3.19 MB}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(}\StringTok{"dplyr"}\NormalTok{)}
\NormalTok{dat <-}\StringTok{ }\KeywordTok{occ_download_import}\NormalTok{(res)}
\NormalTok{dat %>%}
\StringTok{  }\KeywordTok{select}\NormalTok{(gbifID, decimalLatitude, decimalLongitude)}
\CommentTok{#>       gbifID decimalLatitude decimalLongitude}
\CommentTok{#> 1  657590544              NA               NA}
\CommentTok{#> 2  657679551              NA               NA}
\CommentTok{#> 3  657791316        37.70805        -118.4162}
\CommentTok{#> 4  658180562              NA               NA}
\CommentTok{#> 5  441881672              NA               NA}
\CommentTok{#> 6  911596181              NA               NA}
\CommentTok{#> 7   56454601              NA               NA}
\CommentTok{#> 8  657848913              NA               NA}
\CommentTok{#> 9  658187373              NA               NA}
\CommentTok{#> 10 658279212        38.95917        -106.9892}
\CommentTok{#> ..       ...             ...              ...}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{out <-}\StringTok{ }\KeywordTok{occ_search}\NormalTok{(}\DataTypeTok{issue=}\StringTok{'DEPTH_UNLIKELY'}\NormalTok{, }\DataTypeTok{limit =} \DecValTok{500}\NormalTok{)}
\KeywordTok{NROW}\NormalTok{(out)}
\CommentTok{#> [1] 4}
\NormalTok{out %>%}\StringTok{ }\KeywordTok{occ_issues}\NormalTok{(-cudc) %>%}\StringTok{ }\NormalTok{.$data %>%}\StringTok{ }\NormalTok{NROW}
\CommentTok{#> [1] 2}
\end{Highlighting}
\end{Shaded}

@@

\subsubsection{A}\label{a}

\subsubsection{B}\label{b}

\subsubsection{C}\label{c}

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  pt 1
\item
  pt 2
\item
  pt 3
\item
  pt 4
\end{itemize}
